Cluster Analysis Experiments

### 2024-02-02 clustering_analysis.qmd
Added cluster charts to targets pipeline

```{r}
#| echo: false
# Read in the analysis RData file ----
library(factoextra)
library(cluster)
library(dplyr)
library(targets)
library(GGally)
library(gt)
library(tidyverse)

@@

## Next steps?

I wondered about including total list size as a variable?

Other clustering methods?

Other ideas?

>>>>

```{r}
#| echo: false
# Read in the analysis RData file ----
library(factoextra)
library(cluster)
library(dplyr)
library(targets)
library(GGally)
library(gt)
library(tidyverse)
library(targets)

@@

## Five clusters using 14 ethnicities

```{r}
tar_read(elbow_plot)
```

```{r}
tar_read(cluster_plot)
```

```{r}
tar_read(cluster2_chart)
```

```{r}
tar_read(cluster2_map)
```

## Five clusters using 14 ethnicities with % pop 45+

```{r}
tar_read(elbow_plot_over45)
```

```{r}
tar_read(cluster_plot_over45)
```

```{r}
tar_read(cluster1_chart)
```

```{r}
tar_read(cluster1_map)
```
